---
title: "contdistpeter"
author: "Peter Reiker"
date: "11/25/2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contdistpeter currently contains two functions, rejection_sampling and d2_sampler_special.

```{r, include = F}
#library(contdistpeter)
```

## Description for the rejection_sampling Function:

Single variable rejection sampling is the main function of this project.
It recieves a function's pdf and generates a number of samples from the rv with the provided pdf using rejection sampling.
It is thereby somewhat similar to functions such as rbinom, runif, etc.

Input variables:

n is the number of samples to generate.

pdf is the pdf of the random variable you wish to sample from.

a is the lower bound of the random variable you wish to sample from.

b is the upper bound of the random variable you wish to sample from.

C is a numeric such that f(x) <= C for all values of x.

Return variable:

my_sample A vector containg the desired number of random samples from the desired distribution.

## Example:

```{r}
# rejection_sampling(5, function(x)x, 0, sqrt(2), sqrt(2))
```

## Description for the d2_sampler_special Function:

Sampling from a 2D distribution given FX(x) and F(y|X = x) is the additional function of this project.
This function takes samples from a 2D distribution given the marginal pdf of X and the conditional pdf of Y given X = x.
Its output is in the form of a list where a sample from the marginal pdf of X is the first element.

Input variables:

n is the number of samples to generate.

fx is the marginal pdf of X.

fyx is the conditional pdf of Y given X = x (it is in the form function(y,x) expression).

Return Value:

my_samples is a list of samples from the desired 2D distribution.

## Example:

```{r}
# d2_sampler_special(3, function(x) {exp(-x^2/2)/sqrt(2*pi)}, function(y,x){exp(-y^2/2)/sqrt(2*pi)})
```

```{r, fig.show='hold'}

```
