---
title: "contdistpeter"
author: "Peter Reiker"
date: "11/26/2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contdistpeter currently contains two functions, rejection_sampling and d2_sampler_special.

```{r, include = F}
rejection_sampling <- function(n = 1, pdf, a = 0, b = 1, C) {
  # Here I use recursion to obtain the value of a single sample.
  one_sample = function(pdf, a, b, C){
    test_draw = runif(1, a, b)
    if (runif(1, 0, C) <= pdf(test_draw)) return(test_draw)
    return(one_sample(pdf, a, b, C))
  }
  # Here I break the sampling process up using my previously defined function.
  for (i in 1:n){
    if (i == 1) my_samples = one_sample(pdf, a, b, C)
    if (i != 1) my_samples = c(my_samples, one_sample(pdf, a, b, C))
  }
  return (my_samples)
}
d2_sampler_special <- function(n = 1, fx, fyx) {
  # Determine the values to be used with the rejection_sampling function (first time).
  a = 0
  b = 0

  while(integrate(fx, -Inf, a)$value > 1/10^4) a = a - 1
  while(integrate(fx, b, Inf)$value > 1/10^4) b = b + 1

  # Now find an approximate value for C (first time).
  C = optimize(fx, c(a,b), maximum = T)

  one_sample = function(fx, fyx, a, b, C){
  # Now use rejection sampling to find a value of x.
  x = rejection_sampling(1, fx, a, b, C$maximum)

  # Repeat the same process to find a sample from the conditional pdf of Y given X = x.
  fyx_given_x = function(y) fyx(y,x)

  j = 0
  k = 0

  while(integrate(fyx_given_x, -Inf, j)$value > 1/10^4) j = j - 1
  while(integrate(fyx_given_x, k, Inf)$value > 1/10^4) k = k + 1

  D = optimize(fyx_given_x, c(j,k), maximum = T)

  y = rejection_sampling(1, fyx_given_x, j, k, D$maximum)

  # Return the desired sample as a vector.
  return (c(x,y))
  }

  my_samples = list()
  # Here I break up the sampling process using my previously defined function.
  for (i in 1:n) {
    my_samples[[i]] = one_sample(fx, fyx, a, b, C)
  }
  return(my_samples)
}
```

## Description for the rejection_sampling Function:

Single variable rejection sampling is the main function of this project.
It recieves a function's pdf and generates a number of samples from the rv with the provided pdf using rejection sampling.
It is thereby somewhat similar to functions such as rbinom, runif, etc.

Input variables:

n is the number of samples to generate.

pdf is the pdf of the random variable you wish to sample from.

a is the lower bound of the random variable you wish to sample from.

b is the upper bound of the random variable you wish to sample from.

C is a numeric such that f(x) <= C for all values of x.

Return variable:

my_sample A vector containg the desired number of random samples from the desired distribution.

## Examples:

```{r, fig.show='hold'}
sample1 = rejection_sampling(10^4, function(x)1, 0, 1, 1)
sample2 = rejection_sampling(10^4, function(x)2*x, 0, 1, 2)
sample3 = rejection_sampling(10^4, function(x)exp(-x), 0, 10, 1)
hist(sample1)
hist(sample2)
hist(sample3)
```

## Description for the d2_sampler_special Function:

Sampling from a 2D distribution given FX(x) and F(y|X = x) is the additional function of this project.
This function takes samples from a 2D distribution given the marginal pdf of X and the conditional pdf of Y given X = x.
Its output is in the form of a list where a sample from the marginal pdf of X is the first element.

Input variables:

n is the number of samples to generate.

fx is the marginal pdf of X.

fyx is the conditional pdf of Y given X = x (it is in the form function(y,x) expression).

Return Value:

my_samples is a list of samples from the desired 2D distribution.

## Examples:

```{r}
d2_sampler_special(3, function(x) {exp(-x^2/2)/sqrt(2*pi)}, function(y,x){exp(-y^2/2)/sqrt(2*pi)})
d2_sampler_special(3, function(x) {ifelse(x > 0, exp(-x), 0)}, function(y,x){ifelse(0 < y & y < x, 1/x, 0)})
d2_sampler_special(3, function(x) {ifelse(0 < x & x < 1, 1, 0)}, function(y,x){ifelse(0 < y, x*exp(-y*x), 0)})
```
